The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-17 article.tex
Corrcted non-transformed PPC table to transformed

\begin{table}[]
  \caption{Summary statistics of each continuous variable.}\label{tab:summary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cllll@{}}
          \toprule
          \textbf{Variable} & \textbf{Mean} & \textbf{\begin{tabular}[c]{@{}l@{}}Standard\\ Deviation\end{tabular}} & \textbf{Minimum} & \textbf{Maximum} \\ \midrule
          {Yield} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Area Harvested} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Water Used} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Scope One Emissions} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Yield}\over \textbf{Area}$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Average Sale Price} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Average Sale Price} \over \textbf{Area Harvested}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule
          \end{tabular}
  }
  \end{table}
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
        \toprule
        \textbf{Variable} & \textbf{Yield} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{Scope One Emissions} & $\textbf{Yield}\over \textbf{Area}$ & \textbf{Average Sale Price} & $\textbf{Average Sale Price}\over \textbf{Area Harvested}$ \\ \midrule
        \textbf{Yield} & 1.00E+00 & 7.44E-01 & -4.31E-03 & 7.29E-01 & 3.50E-01 & -2.26E-01 & -1.64E-01 \\
        \textbf{Area Harvested} & 7.44E-01 & 1.00E+00 & -5.33E-03 & 8.92E-01 & 7.85E-02 & -1.18E-01 & -2.04E-01 \\
        \textbf{Water Used} & -4.31E-03 & -5.33E-03 & 1.00E+00 & -1.93E-03 & -5.60E-03 & -3.56E-02 & -2.67E-02 \\
        \textbf{Scope One Emissions} & 7.29E-01 & 8.92E-01 & -1.93E-03 & 1.00E+00 & 9.36E-02 & -9.42E-02 & -1.93E-01 \\
        $\textbf{Yield}\over \textbf{Area}$ & 3.50E-01 & 7.85E-02 & -5.60E-03 & 9.36E-02 & 1.00E+00 & -4.85E-01 & -1.70E-01 \\
        \textbf{Average Sale Price} & -2.26E-01 & -1.18E-01 & -3.56E-02 & -9.42E-02 & -4.85E-01 & 1.00E+00 & 4.73E-01 \\
        $\textbf{Average Sale Price} \over \textbf{Area Harvested}$ & -1.64E-01 & -2.04E-01 & -2.67E-02 & -1.93E-01 & -1.70E-01 & 4.73E-01 & 1.00E+00 \\ \bottomrule
        \end{tabular}
}
\end{table}
Pearson Correlation Coefficients of the transformed, centered and scaled variables are shown in Table \ref{tab:pearson_correlation}. 
\par
All relationships were found to be statistically significant (P $<$ 2.200E-16).
\subsection{General Linear Models}

>>>>

\begin{table}[]
  \caption{Summary statistics of each continuous variable.}\label{tab:summary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cllll@{}}
          \toprule
          \textbf{Variable} & \textbf{Mean} & \textbf{\begin{tabular}[c]{@{}l@{}}Standard\\ Deviation\end{tabular}} & \textbf{Minimum} & \textbf{Maximum} \\ \midrule
          {Yield} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Area Harvested} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Water Used} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Scope One Emissions} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Yield}\over \textbf{Area}$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          {Average Sale Price} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\
          \multicolumn{1}{l}{} &  &  &  &  \\
          ${Average Sale Price} \over \textbf{Area Harvested}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule
          \end{tabular}
  }
  \end{table}
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
          \textbf{} & \textbf{Yield} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}} & \textbf{Average Price} & \textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}} \\ \midrule
          Yield & 1.00 & 0.75 & 0.00 & 0.72 & 0.35 & 0.40 & -0.23 \\
          Area Harvested & 0.75 & 1.00 & -0.01 & 0.88 & 0.09 & 0.86 & -0.13 \\
          Water Used & 0.00 & -0.01 & 1.00 & 0.00 & -0.01 & 0.05 & -0.03 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.72 & 0.88 & 0.00 & 1.00 & 0.10 & 0.75 & -0.10 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.35 & 0.09 & -0.01 & 0.10 & 1.00 & -0.09 & -0.48 \\
          Average Price & 0.40 & 0.86 & 0.05 & 0.75 & -0.09 & 1.00 & 0.07 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.23 & -0.13 & -0.03 & -0.10 & -0.48 & 0.07 & 1.00 \\ \bottomrule
          \end{tabular}
}
\end{table}
Pearson Correlation Coefficients of the transformed, centered and scaled variables are shown in Table \ref{tab:pearson_correlation}. 
\par
All relationships were found to be statistically significant (P $<$ 2.200E-16).
\subsection{General Linear Models}
